---
title: "Homework 5"
author: "Pavithra Srinivasan"
date: November 16, 2023
output: github_document
---


```{r setup, include=FALSE}
library(tidyverse)
library(haven)
library(readxl)
library(dplyr)
library(tidyr)
library(broom)
library(rvest)
library(purrr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

Assignment Due: November 16th 

## Problem 1

Discussed in class, and solution already provided. 

## Problem 2

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time: 

Iterate file names and read in data for each subject and clean it:
```{r}

file_names = list.files(path = "./data1", full.names = TRUE)

#Import and combining files

tidy_df = file_names |> 
  map_dfr(read_csv, .id = "participant_id") |> 
  mutate(study_arm = print(dir(path = "./data1", include.dirs = FALSE))) |> 
  mutate(study_arm = str_remove(study_arm, ".csv")) |> 
  separate(study_arm, into = c("study_arm", "subject_id")) |> 
  select(participant_id, study_arm, subject_id, everything())

tidy_df |> 
  knitr::kable(digits = 2)

#Cleaning

tidy_df = tidy_df |> 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observations",
    names_prefix = "week_"
  ) |> 
  mutate(week = as.numeric(week))

tidy_df |> 
  head()

```

### Lets Visualize by creating a spaghetti plot

```{r}

spaghetti_plot = tidy_df |>
  group_by(subject_id) |> 
  ggplot(aes(x = week, y = observations)) + 
           geom_point(alpha = 0.7, aes(color = subject_id)) +  geom_line(alpha = 0.7, aes(color = subject_id)) +
          geom_smooth() +
  labs(
    title = "Observations of study participants over 8 weeks",
    x = "Week",
    y = "Observations"
  ) +
  facet_grid(. ~ study_arm)

spaghetti_plot
```

Interpretation: The Control arm is more constant for all the participants over the course of the 8 weeks. Whereas, there is an increase in the number of observations in the Experimental arm especially from week 2. Participant 4 had the most fluctuations in both the control and experimental groups, and participant 10 had the most erratic fluctuations in the experiment group. 

## Problem 3
n = 30
sigma = 5
alpha = 0.05

```{r}
set.seed(123)
```

Generate 5000 datasets from the model:

```{r}
sim_function = function(mu) {
  sim_data = tibble(rnorm(n = 30, mean = mu, sd = 5))
  
  sim_data |> 
    t.test() |> 
    broom::tidy() |> 
    select(estimate, p.value)
}

results = 
  expand_grid(
    mu = 0,
    iter = 1:5000) |> 
  mutate(estimate_df = map(mu, sim_function)) |> 
  unnest(estimate_df)
```

Repeat the above for μ={1,2,3,4,5,6}:
```{r}
results_2 = expand_grid(mu = 1:6, iter = 1:5000) |> 
  mutate(estimate_df = map(mu, sim_function)) |> 
  unnest(estimate_df)
```

#### Visualization:

Plot 1: proportion of times the null was rejected 

```{r}
null_plot = 
  results_2 |> 
  filter(p.value < 0.05) |> 
  group_by(mu) |> 
  summarize(
    total_n = n()) |> 
  mutate(
    reject_null = total_n/5000
  ) |> 
  ggplot(aes(x = mu, y = reject_null)) + 
    geom_line() + 
    labs(
      title = "True Effect Size and Power",
      x = "Mean",
      y = "Proportion of Times the Null was Rejected")

null_plot
```
Interpretation: Plot shows the number of times the null hypothesis was rejected, since the p-value was greater than 0.05. The mean increases with the rejection of the null. 

Plot 2: Make a plot showing the average estimate of μ^ on the y axis and the true value of μ
 on the x axis. Make a second plot (or overlay on the first) the average estimate of μ^
 only in samples for which the null was rejected on the y axis and the true value of μ
 on the x axis.

```{r}
mu_plot = 
  results_2 |> 
  group_by(mu) |> 
  summarize(
    avg_mu = mean(estimate),
    avg_mu_reject = mean(estimate[p.value < 0.05])
  ) |> 
  pivot_longer(
    cols = starts_with("avg"),
    names_to = "mu_plot",
    values_to = "mean_estimate"
  ) |> 
  ggplot(aes(x = mu, y = mean_estimate, color = mu_plot)) + 
  geom_point() +
 labs(
    x = c("True Mean "),
    y = c("Estimate"),
    caption = c("Effect of mu on true and estimate mean")
  )
mu_plot
```
Interpretation: This plot shows the average mean estimates of samples, and also for specifically samples in which the null was rejected. The average mean estimate across tests for which the null was rejected is further away from the true mean. It looks like as the effect size gets larger the average  estimate values get closer to the true mean. 
